Digital History in Finland, 1488-1828

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r summaryTop10authorstimeline, fig.height=6, fig.width=10, echo=FALSE, fig.show="hold", out.width="430px"}
theme_set(theme_bw(20))
for (catalogue in c("Fennica", "Kungliga")) {
  df <- filter(df0, catalog == catalogue)
  top.authors <- names(top(df, field = "author", n = 3))
  dfs <- df %>% filter(author %in% top.authors) %>%
     	 group_by(author, publication_decade) %>%
     	 tally() %>%
     	 arrange(publication_decade)
  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle(paste("Title count top authors\n", catalogue)) +
       xlim(range(df0$publication_year))
  print(p)
}
```

@@

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

>>>>

```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r summaryTop10authorstimeline, fig.height=4, fig.width=10, echo=FALSE, fig.show="hold", out.width="430px"}
theme_set(theme_bw(20))
for (catalogue in c("Fennica", "Kungliga")) {
  df <- filter(df0, catalog == catalogue)
  top.authors <- names(top(df, field = "author", n = 3))
  dfs <- df %>% filter(author %in% top.authors) %>%
     	 group_by(author, publication_decade) %>%
     	 tally() %>%
     	 arrange(publication_decade)
  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle(paste("Title count top authors\n", catalogue)) +
       xlim(range(df0$publication_year))
  print(p)
}
```

@@

```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {

@@

```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
# TITLE COUNT
for (catalogue in c("Fennica", "Kungliga")) {
